\section{Subsystems}

The main subsystems required of each of our cubesat are:

\subsection{Communication}
The communication subsystem allows us to realize the reception and trasmission of data, voice signals, etc. It consists of a group of transponders, that are the combination of a transmitter and a receiver and whose functions are receiving, separating, amplify, process, reamplify and retransmit signals.

The telemetry subsytem analyses the information about the ground station and other sensors of the satellite in 	order to monitor conditions on board. It allows report to ground station about the conditions of the on board systems.

The command and control subsystem allows the ground station to control the satellite.
	
\subsection{Electrical power system}
The principal electrical power system  goal is storing and distributing power to the different subsystems of the satellite.

Solar arrays are the principal power source of the satellite and generate a current that is used to allow the functioning the the other components of the satellite.

Batteries give power the different subsystems when solar arrays do not, due to not receiving sunlight
	
\subsection{Thermal protection}
The thermal protection system protect the CubeSat from thermal shocks. The satellite must remain in a optimal range of temperatures,despite the external temperature. It consists of various insulating materials and thermal conductors in order to maintain it within acceptable temperatures.

\subsection{Attitude and orbital control system}
Attitude and orbital control subsystem is needed to enable the satellite to keep a specific position within its orbit and to control the antennas in order to remain oriented to assigned area, because the satellite tends to change its orientation due to torque. The AOCS receives telecommands from the central computer and acquires measurements (satellite attitude and orbital position) from sensors.

%\subsubsection{Propulsion?}
%
%\subsubsection{Payload?}