\section{Marketing Plan}
\subsection{Executive Summary}
Astrea is the result of an enormous amount work and effort from its 17 co-founders and its name needs to be spread all over the world in order to start selling its services. In order to do that it is important to define the target customers to whom the service offered is going to be sold. Being the latter clear, it's essential to point out what does Astrea offer that makes it stand out from the rest of companies in the sector, that is, making an assessment of the strong points of the company. Moreover, it is necessary to establish the price at which the service is going to be sold to the customers and defining the position of the company among its competitors in the sector.
\newline\newline
Of course none of the above would make sense without defining a distribution plan in which the way customers buy from us is defined. In addition to that, the marketing materials used also have to be defined along with the online marketing strategy.
\newline\newline
A conversion strategy has to be defined too, that is, defining a way to turn prospective customers into paying ones. Finally, possible partnerships or future partnership plans will be assessed.
\subsection{Target Customers}
One of the most important items when it comes to selling a product or service is to whom it may be of interest. Since the service sold is essentially a communication bridge between satellite-to-satellite, Earth-to-satellite or Earth-to-Earth, it is well obvious that the average customer is not going to be an average consumer.
\newline\newline
Instead the service offered is projected towards public or private institutions such as aerospace universities who would like to execute experiments which require a reliable communication between their own spacecraft and their ground stations. Also towards start-up enterprises who would like to enter into the aerospace industry and need Astrea's infrastructure to accomplish their own projects.
\newline\newline
In addition to all of the above, the service is also targeted towards space agencies who plan on doing pilot missions with which Astrea could help with. Also aerospace enterprises who nonetheless would like to test their technologies and need real time feedback from them. Finally another targeted sector would be the communications enterprises who would like to acquire real time information from Earth's surface or outer space.
\subsection{Unique Selling Proposition}
The USP is, as the title appoints, what Astrea has to offer that sets it apart from other companies in its sector. Everyone in Astrea knows what the company is capable of and what it can offer and this is no more and no less than:
\begin{itemize}
\item Global signal coverage: Astrea's constellation covers every single spot on Earth's surface. This means that every ground station will have full-time signal coverage.
\item Ground station support: Astrea offers ground stations to its customers. For advanced users, custom ground stations are also available.
\item High reliability: Astrea's constellation is robust. Therefore, reliability is guaranteed.
\item Cheapest price on sector: Astrea brings global communication to customers at the lowest and most affordable price.
\end{itemize}
\subsection{Pricing \& Positioning Strategy}
The communication service Astrea offers is set to a price of 0.1\euro /Mb. Since there are no other companies offering the same kind of service it is not possible to make a comparison as of now. 

\subsection{Distribution Plan}
Since what Astrea offers is not a conventional service, people will not be able to purchase it directly. Instead, we use our website to get people to know what Astrea does as well as a way for our customers to get in touch with us. When a customer contacts us we provide them with all the necessary information on how to properly use our systems. Once the contract is made they can start using our communication systems right away. The payment is done monthly much like a regular mobile carrier. Customers will get their invoices with their total data consumption and price.

\subsection{Marketing Materials}
The marketing materials we count on are:
\begin{itemize}
\item A website: http://astrea.upcprogram.space/
\item An informative and encouraging video.
\item Brochures.
\item A poster.
\end{itemize}

\subsection{Online Marketing Strategy}
Given the fact that our distribution plan is executed in an essentially online manner, it makes sense to elaborate an Online Marketing Strategy. The key components to our online marketing strategy are:
\begin{enumerate}
\item Keyword Strategy: it is important to identify the keywords to optimize our website for. In our case the keywords would be: "Astrea", "constellation", "reliability", "CubeSat" and "communication".
\item Search Engine Optimization: document updates will be made to the website in order to appear more prominently in online search engines.
\item Social Media Strategy: nowadays it is crucial to be in the social media. The world is permanently connected through the social media and it can be one of most powerful ways to show off what we've produced. Therefore, Astrea will have its own Twitter, Instagram and Facebook accounts.
\end{enumerate}
\subsection{Conversion Strategy}
The technique we use to turn prospective customers into actual paying customers will be showing testimonials from actual customers were were satisfied with our service in our website. In addition to that, we will post in our website every successful project we provide service to. This will show the reliability of the service to the insecure customers and hopefully turn them into actual customers
\subsection{Joint Ventures \& Partnerships}
Right at its beginning Astrea does not count on any Joint Ventures nor Partnerships with other enterprises. Nevertheless, Astrea is open to future partnerships with businesses who would like to work in collaboration with us.