\subsection{Salaries}

\paragraph{}In order to work properly, each ground station will require an electrical engineer, a computer technician, a manager and a secretary. Due to the nature of the constellation, the GS will need to be always functioning and, therefore, it can potentially fail at any moment. For this reason, the presence of an electrical engineer and a computer technician is required all the time. Four engineers and four computer technician will be hired so that for each job three of them will work all the day in 8 hours shifts while the other has the day off.

\paragraph{}The salaries for each employee will be the average salary for each job in their respective countries. Those can be seen in Figure \ref{table:Salaries}.

\begin{table}[H]
\begin{center}
\begin{tabular}{|l|r|r|r|}
\hline 
 & Canada & United Kingdom & Argentina \\ 
\hline 
Electrical engineer & 47,700\euro & 36,900\euro & 12,300\euro \\ 
\hline 
Computer technician & 30,100\euro & 21,800\euro & 7,100\euro \\ 
\hline 
Manager & 34,500\euro & 28,800\euro & 14,100\euro \\ 
\hline 
Secretary & 28,000\euro & 22,300\euro & 9,500\euro \\ 
\hline 
\end{tabular}
\end{center}
\caption[Salaries according to country]{Salaries for the different jobs according to the country.}
\label{table:Salaries}
\end{table}

\paragraph{}Taking into account that each GS will have a manager, a secretary, four electrical engineers and four computer technicians, and that everyday will be an engineer and a technnician working during night, the total cost per ground station would be the following:
\begin{itemize}
\item Canada: 381,500\euro
\item United Kingdom: 226,400\euro
\item Argentina: 81,800\euro
\end{itemize}

\paragraph{}The Mission Control Centre will consist of a building with a manager, a secretary and three aerospace engineers working. Because of the same reason as the ground station, it will be needed to hire twelve engineers, so as to have always three of them working all the time. Taking into account the average salary of each job in Spain, the cost of the salaries can be seen in Figure \ref{table:SalariesSpain}:

\begin{table}[H]
\begin{center}
\begin{tabular}{|l|r|}
\hline 
 & Spain \\ 
\hline 
Aerospace engineer & 30,600\euro \\ 
\hline 
Manager & 30,500\euro  \\ 
\hline 
Secretary & 23,000\euro  \\ 
\hline 
\end{tabular}
\end{center}
\caption[Salaries in Spain]{Salaries for the different jobs in Spain.}
\label{table:SalariesSpain}
\end{table}

\paragraph{}The annual cost of all the salaries can be seen below:
\begin{itemize}
\item Annual cost of all Ground Stations salaries: 689,700\euro
\item Annual cost of the Mission Control Centre salaries: 429,900\euro
\end{itemize}

\paragraph{}Finally,with the frequency fees, the maintenance and the salaries, the total annual cost of all the ground segment canbe obtained.
\begin{itemize}
\item Annual cost of the ground segment: 1,200,000\euro
\end{itemize}