In this subsection the decision between building GS or renting existent ones will be taken. There are a few things to be taken into account before starting to talk about the benefits and drawbacks of each of the options.

First of all, the number of ground stations required is needed. If there is no communication with the satellites, the mission would not be accomplished. For this reason, the nodes of the ground stations are very important. The number of ground stations required is the minimum number that, with two failures, which is one of the requirements, can still transfer the data from the satellite of the client to the client itself in less than 5 minutes. Supposing that three ground stations are built or rent, if two of them fail the communication between the client and its satellite can still be done using the left ground station. Therefore, \textbf{three Ground Stations} are needed.

Regarding the latency, as it has been already exposed, the communication will take place with a latency of less than 5 minutes, as only one ground station that may fall will be in the communication path and is very improbable that if the ground station fails and the information is redirected to another, the latter falls too in less than three minutes. Regarding the position of the ground station, as the code developed shows, the ideal will be to have them near to a latitude of 60ยบ, because they would be capable to stablish more links with different satellites and then the communication to the client's satellite is assured.

The decision will be performed using an Ordered Weighted Average method (OWA) that can be found in \cite[Chapter 3, Section 5]{annex3}. The conclusion of the decision process are explained in the following lines:

\subsubsection{Decision}
The results of the OWA have been the following ones:
\begin{itemize}
\item Building a GS: 0.83
\item Renting a GS: 0.67
\end{itemize}

Looking at the results, building a ground station is the best option for Atrea Constellation in order to accomplish its requirements and to give a high-quality service.