\section{Internal Structure}


\subsection{Hierarchy}

In order to build a work strategy, the project is divided in tasks that will be described later on. As the different tasks depend on each other, the project members have decided to follow a hierarchy. Every task is developed by a small team between 2 and 5 people depending on the amount of work the task requires.
\newline

Each small team has to have a coordinator which has two principal functions. The first one is to manage the group so he / she is responsible for the good organisation and progression of the task. The second is that he / she is the voice of the team. That means that the coordinator is the one who represents his / her work team when transferring information to the other group coordinators and the project managers and vice versa.
\newline

Over all the teams Boyan Naydenov is the project manager who ensures the project progress and manages people for major decisions. Finally, Silvia Gonz\'{a}lez is the secretary in charge to write and delivery the minutes and agendas of each meeting. She is also in charge of the organization and storage of all the documents in BSCW. \newline
 
\begin{table}[h]
\begin{tabular}{ | l | l | p{5cm} |}
\hline
\textbf{Department} & \textbf{Coordinator} & \textbf{Team members} \\ \hline
Orbits Design & Oscar Fuentes Muñoz & Llu\'{i}s Foreman Campins\\ \hline
 & & S\'{i}lvia Gonz\'{a}lez Garc\'{i}a \\ \hline
 & & V\'{i}ctor Mart\'{i}nez Viol \\ \hline
 & & Laura Pla Olea \\ \hline
Satellite Design & Pol Fontanes Molina & Fernando Herr\'{a}n Albelda \\ \hline
 & & David Morata Carranza \\ \hline
Communications & Eva Mar\'{i}a Urbano Gonz\'{a}lez & Boyan Naydenov \\ \hline
 & & Josep Puig Ruiz \\ \hline
 & & Josep Mar\'{i}a Serra Moncunill \\ \hline
 & & Sergi Tarroc Gil \\ \hline
Constellation Deployment & Xavi Ti\'{o} Malo & Joan Cebri\'{a}n Gal\'{a}n \\ \hline
 & & Roger Fraixedas Lucea \\ \hline
 & & Marina Pons Daza \\ \hline

\end{tabular}
\caption{Roles and Responsabilities}
\end{table}
\subsection{Documents organisation}


The Astrea team has \textbf{17 members} so it is essential to define a protocol to organise all the documents and information found to take advantage of resources. 
\newline

The main internal communication tool used is \textit{Slack} which is a platform specialised in team communication. \textit{Slack} defines itself as a real-time messaging, achieving and searching tool for modern teams which is interesting for us because it allows the group to communicate at all times for punctual doubts and small decisions. For major decisions a meeting date will be specified using doodle. Communication between the customer and project manager will be carried out via e-mail. Weekly meetings with the customer are scheduled every Thursday and will be formalised through the agenda.
 \newline

Moreover, to share documents we use two platforms: \textit{Slack} and \textit{BSCW}. On Slack we put first drafts or documents that can be interesting. \textit{BSCW} is the main information storage because information and documents are stocked and organised in folders. 
\newline

At last, the text editor used to develop the project is \textit{Latex} which combined with G\textit{it} allows us to work remotely on a same document without overriding someone else's work. This work system is really interesting for such a big group in order to work on the same document while keeping a record of the changes.