\subsection{Description of the tasks}
\begin{longtable}{ | p{1.3cm} | p{3cm} | p{11cm} |}
\hline
\textbf{ID} & \textbf{Work Package} & \textbf{Biref task description list} \\ 
\hline
\multicolumn{3}{|c|}{\textbf{1.Managment}} \\ \hline
1.1 & Meetings Documents & 

\underline{\textbf{·}Writing agendas of the meetings:}   

The team’s secretary will take note of the topics pending to debate and make a list to be checked by the team. \newline
\underline{\textbf{·}Writing minutes of the meetings:} 

The team’s secretary will take note of the debate and conclusions of the meeting.\\ \hline

1.2 & Task tracking and scheduling & 

\underline{\textbf{·}Project Charter:}

A description of the project to develop is going to be detailed by all the group members during the first weeks. \newline
\underline{\textbf{·}Team tasks monitoring:}

The coordinator will ensure tasks compliance and register the progress.\newline
\underline{\textbf{·}WBS and Gantt update:}

The documents summarizing the project organization will be updated with final dates and final topics assessed.
\\
\hline
\multicolumn{3}{|c|}{\textbf{2. Satellite}} \\ \hline
2.1 & Spacecraft Subsystems &  \textbf{·}Establishment of requirements once orbits are defined. \newline
\textbf{·}External enterprise hiring for hardware and software design.
\\ \hline
2.2.1 & Payload antenna &  \textbf{·}Calculation of the size of the antenna needed to communicate with the other satellites. \newline
\textbf{·}Search the available antenna in the market that best fits the needs of the project.
\\
\hline
2.2.2 & Payload Data Handling System (PDHS) &  \textbf{·}Selection of the configuration. \newline
\textbf{·}Establishment of the desired hardware and software.
\newline
\textbf{·}Search the available PDHS in the market that best fits the needs of the project.
\\
\hline
\multicolumn{3}{|c|}{\textbf{3. Constellation}} \\ \hline
3.1 & Constellation geometry & \underline{\textbf{·}Number of satellites:} It is necessary to determine the total number of satellites in order to get global coverage. \newline
\underline{\textbf{·}Distribution of the satellites:} Compute the correct distribution of these satellites. \\
\hline
3.2.1 & General parameters & \underline{\textbf{·}Parameter description:} Physical definition of the orbits for each satellite of the constellation. \\ \hline
3.2.2 & Drifts & \underline{\textbf{·}Orbit modifications:} Compute the possible orbit deviations of the different satellites. \\ \hline
3.3 & Legislation & \underline{\textbf{·}Research:} Study the legislation referred to nanosatellites. \newline
\underline{\textbf{·}Implement:} Apply the necessary measures to accomplish the legal requirements. \\ \hline
\multicolumn{3}{|c|}{\textbf{4. Launch Systems}} \\ \hline
4.1 & Vehicle  & \textbf{·}Study of the requirements for the launch of the cubesats. \newline
\textbf{·}Research of the main companyies that offer launch services, including their features and costs. \newline
\textbf{·}Decision of the best launch system for our goal, regarding the requirements and the available technology. \\ \hline
4.2 & Satellite Deployer & \textbf{·}Study of the requirements for the launch of the cubesats. \newline
\textbf{·}Research of the deployment systems that the main companies offer. \newline
\textbf{·}Decision of the best launch system for our goal, regarding the requirements and the available technology. \\ \hline
\multicolumn{3}{|c|}{\textbf{5. Operations}} \\ \hline
5.1 & Communication protocol & \textbf{·}Study the existing communication protocols. \newline
\textbf{·}Adapt the existing protocols or create new ones. \\ \hline
5.2 & Ground station & \textbf{·}Determine the number of ground stations needed. \newline
\textbf{·}Design a model of a ground station capable
of communication efectively with the constellation.\\ \hline
5.3 & End of life strategy & \textbf{·}Study the existing end of life protocols. \newline
\textbf{·}Choose the protocol that applies to the satellites. \\
\hline
\multicolumn{3}{|c|}{\textbf{6. Financial Plan}} \\
\hline
6.1.1.1 & Maintenance cost analysis &  
\textbf{·}Determine maintenance costs related to the constellation and the ground station.\\ 
\hline
6.1.1.2 & Insurance cost analysis &  
\textbf{·}Study of the insurance market and choosing the best option.\\ 
\hline
6.1.1.3 & Administration cost analysis & 
\textbf{·}Determine how much it will cost to manage the constellation.\\ 
\hline
6.1.1.4 & Taxes cost analysis  & 
\textbf{·}Analysis of taxes related to the service provided and how it will affect the economic balance.
\\ 
\hline
6.1.2.1 &  Manufacturing cost report & 
\textbf{·}Determine the cost of production of the different elements of the constellation.\\ 
\hline
6.1.2.2 & Launching cost report & 
\textbf{·}Study of the best options in the market to launch the satellites and choosing one of them.\\ 
\hline
6.2.1 & Price analysis &   
\textbf{·}Determine the price of the service provided for optimum income.\\ 
\hline
6.2.2 & Revenue forecast & 
\textbf{·}Study of the demand for the service provided.\\ 
\hline
6.3 & Economic feasibility report & 
\textbf{·}Study of the costs and income of the project to determine if it can carry out.\\ 
 \hline
 \multicolumn{3}{|c|}{\textbf{7. Project Exhibition}} \\ \hline
7 & Project Exhibition & 

\underline{\textbf{·}Perform a simulation of the constellation} in order to show how it will work \\ \hline
\caption{Tasks Description} \\
\end{longtable}